---
title: "ana_open"
author: "hyl"
date: "2025-04-11"
output: html_document
---
#0.1Formula and package preparation
```{r setup, include=FALSE}
install.packages("pacman")
library(pacman)
p_load(haven,mice,survey,dplyr,tibble,knitr,tidyverse,tidyfst,lattice,tableone,writexl,table1,readxl,survminer,foreign,car,sjmisc,nricens,openxlsx,Hmisc,ggtext,patchwork,ggplotify,cowplot,labelled,WeightIt,forestplot,gridExtra,cobalt,PSweight,lme4,geepack,MatchIt,flexsurv,boot,rstpm2,rms,data.table)

# Export formatting adjustments
export_to_excel <- function(data, file, sheet) {
  if (file.exists(file)) {
    wb <- loadWorkbook(file)
    if (tolower(sheet) %in% tolower(names(wb))) {
      removeWorksheet(wb, sheet)
    }
  } else {
    wb <- createWorkbook()
  }
  addWorksheet(wb, sheet)
  writeData(wb, sheet, as.data.frame(data), rowNames = TRUE) 
  saveWorkbook(wb, file, overwrite = TRUE)
}

rate_diff_func <- function(data, indices) {
  # Get bootstrap samples
  sample_data <- data[indices, ]
  # Recalculate the weighted mortality rate
  weighted_case_mortality <-  weighted.mean(sample_data$death_lm[sample_data$case_control == 1], sample_data$weight[sample_data$case_control == 1])
  weighted_control_mortality <- weighted.mean(sample_data$death_lm[sample_data$case_control == 0], sample_data$weight[sample_data$case_control == 0])
  
  rate_difference_bh <- weighted_case_mortality - weighted_control_mortality
  return(rate_difference_bh)
}
calculate_weighted_mortality_rate_difference <- function(data) {
  # Calculate the weighted mortality rate for the case group
  weighted_case_mortality <- weighted.mean(data$death_lm[data$case_control == 1], data$weight[data$case_control == 1])
  
   # Calculate the weighted mortality rate for the control group
  weighted_control_mortality <- weighted.mean(data$death_lm[data$case_control == 0], data$weight[data$case_control == 0])
  # Calculate mortality differences
  rate_difference <- weighted_case_mortality - weighted_control_mortality
  
  # Return a list of results
  return(data.frame(weighted_case_mortality = weighted_case_mortality,
                    weighted_control_mortality = weighted_control_mortality,
                    rate_difference = rate_difference))
}


```
#1.1 Matching using SAS code
```{SAS Code}
#For all STEMI patients
proc psmatch data=merged_data;
    class sex case_control;  /* Ensure full gender match */
    psmodel case_control(treated='1') = age sex;  
    /* Using the Mahalanobis distance, set the matching distance to age */
    match method=greedy(k=5) exact=sex caliper=0.2 weight=ATTWGT;
	assess lps var=(age sbp hyp)/varinfo weight=ATTWGT stddiff plots=none;
    output out(obs=match)=drv2.matched_data1 matchid=matchid;
run;

#For STEMI patients treated with PPCI
proc psmatch data=Mdata_ppci;
    class sex case_control;  
    psmodel case_control(treated='1')  = age sex;  
    match method=greedy(k=5) exact=sex caliper=0.2 weight=ATTWGT;
    output out(obs=match)=drv2.matched_data2 matchid=matchid;
run;

#For STEMI patients treated with fibrinolysis
proc psmatch data=Mdata_fibri;
    class sex case_control;  
    psmodel case_control(treated='1')  = age sex;  
    match method=greedy(k=5) exact=sex caliper=0.2 weight=ATTWGT;
    output out(obs=match)=drv2.matched_data3 matchid=matchid;
run;

#For STEMI patients treated with conservative therapy
proc psmatch data=Mdata_bs;
    class sex case_control;  
    psmodel case_control(treated='1')  = age sex;  
    match method=greedy(k=5) exact=sex caliper=0.2 weight=ATTWGT  ;
    output out(obs=match)=drv2.matched_data4 matchid=matchid;
run;

```
#1.2.1 STEMI: split datasets by time
```{r}
#landmark1, in days 0-30
LM1<-matched_data1 %>% mutate(FUds= case_when(
      followupday <=30 ~ followupday ,
      followupday  >30 ~ 30,
      TRUE ~ NA),
      FUds=if_else(FUds==0,0.0001,FUds),
    death_lm = case_when(
     followupday >30 & death == 1 ~ 0,
      TRUE ~ death)
    )%>% group_by(matchid) %>% 
  mutate(matchid_size = n()) %>% 
  ungroup() %>% mutate(weighgt=ifelse(case_control==0,1 /(matchid_size-1),1))


#landmark2, within 30-90 days
LM2 <- matched_data1 %>%
  # Mark if case dies within 30 days
  mutate(case_to_remove = ifelse(case_control == 1 & followupday <= 30 & death == 1, 1, 0)) %>%
  # Flag each matchid for the presence of cases that died within 30 days
  group_by(matchid) %>%
  mutate(case_to_remove_matchid = max(case_to_remove, na.rm = TRUE)) %>%
  ungroup() %>%
  # Delete matchid with cases that died within 30 days
  filter(case_to_remove_matchid == 0) %>%
  # Marker whether control died within 30 days
  mutate(control_to_remove = ifelse(case_control == 0 & followupday <= 30 & death == 1, 1, 0)) %>%
  # For each matchid control, check if all controls die within 30 days
  group_by(matchid) %>%
  mutate(all_controls_dead_30days = max(control_to_remove, na.rm = TRUE)) %>%
  # If all controls in a matchid are dead, mark the entire matchid as needing to be deleted.
  mutate(remove_whole_matchid = ifelse(all_controls_dead_30days == 1, 1, 0)) %>%
  ungroup() %>%
  # Delete matchid where all controls died within 30 days (including cases)
  filter(remove_whole_matchid == 0) %>%
  # Create follow-up days and amended death markers
  mutate(FUds = case_when(
    followupday <= 90 ~ followupday,
    followupday > 90 ~ 90,
    TRUE ~ NA_real_  # Ensure NA type is correct
  ),
  death_lm = case_when(
    followupday > 90 & death == 1 ~ 0,  # Time to death over 90 days set to 0
    TRUE ~ death
  ))%>% group_by(matchid) %>% # Calculate the number of each matchid
  mutate(matchid_size = n()) %>% 
  ungroup() %>% mutate(weight=ifelse(case_control==0,1 /(matchid_size-1),1))

# 90days to 1 year
LM3 <- matched_data1 %>%
  # Create a new variable to mark if a case died within 90 days
  mutate(case_to_remove = ifelse(case_control == 1 & followupday <= 90 & death == 1, 1, 0)) %>%
  # Flag each matchid for the presence of cases that died within 90 days
  group_by(matchid) %>%
  mutate(case_to_remove_matchid = max(case_to_remove, na.rm = TRUE)) %>%
  ungroup() %>%
  # Delete matchid with cases that died within 90 days
  filter(case_to_remove_matchid == 0) %>%
  # Mark if all controls die within 90 days
  mutate(control_to_remove = ifelse(case_control == 0 & followupday <= 90 & death == 1, 1, 0)) %>%
  # For each matchid control, check if all controls died within 90 days
  group_by(matchid) %>%
  mutate(all_controls_dead_90days = max(control_to_remove, na.rm = TRUE)) %>%
   # If all controls in a matchid are dead, mark the entire matchid as needing to be deleted.
  mutate(remove_whole_matchid = ifelse(all_controls_dead_90days == 1, 1, 0)) %>%
  ungroup() %>%
  # Delete matchid where all controls died within 90 days (including cases)
  filter(remove_whole_matchid == 0) %>% 
  mutate(FUds=followupday,death_lm=death)%>% group_by(matchid) %>% # Calculate the number of each matchid
  mutate(matchid_size = n()) %>% 
  ungroup() %>% mutate(weight=ifelse(case_control==0,1 /(matchid_size-1),1))

#0- 1year
LM_3_1 <- matched_data1 %>% mutate(FUds= case_when(
      followupday <=365 ~ followupday ,
      followupday  >365 ~ 365,
      TRUE ~ NA),
      FUds=if_else(FUds==0,0.0001,FUds),
    death_lm = case_when(
     followupday >365 & death == 1 ~ 0,
      TRUE ~ death)
    )%>% group_by(matchid) %>% 
  mutate(matchid_size = n()) %>% 
  ungroup() %>% mutate(weight=ifelse(case_control==0,1 /(matchid_size-1),1))

#1y-5y
LM_3_2 <- matched_data1 %>%
  mutate(case_to_remove = ifelse(case_control == 1 & followupday <= 365 & death == 1, 1, 0)) %>%
  group_by(matchid) %>%
  mutate(case_to_remove_matchid = max(case_to_remove, na.rm = TRUE)) %>%
  ungroup() %>%
  filter(case_to_remove_matchid == 0) %>%
  mutate(control_to_remove = ifelse(case_control == 0 & followupday <= 365 & death == 1, 1, 0)) %>%
  group_by(matchid) %>%
  mutate(all_controls_dead_90days = max(control_to_remove, na.rm = TRUE)) %>%
  mutate(remove_whole_matchid = ifelse(all_controls_dead_90days == 1, 1, 0)) %>%
  ungroup() %>%
  filter(remove_whole_matchid == 0) %>% 
  mutate(FUds=followupday,death_lm=death)%>% group_by(matchid) %>%
  mutate(matchid_size = n()) %>% 
  ungroup() %>% mutate(weight=ifelse(case_control==0,1 /(matchid_size-1),1))

# 0-90 days
LM4<-matched_data1 %>% mutate(FUds= case_when(
      followupday <=90 ~ followupday ,
      followupday  >90 ~ 90,
      TRUE ~ NA),
      FUds=if_else(FUds==0,0.0001,FUds),
    death_lm = case_when(
     followupday >90 & death == 1 ~ 0,
      TRUE ~ death)
    )%>% group_by(matchid) %>% 
  mutate(matchid_size = n()) %>% 
  ungroup() %>% mutate(weight=ifelse(case_control==0,1 /(matchid_size-1),1))


cox_model_clustered1 <- coxph(Surv(FUds, death_lm) ~ case_control, data = LM1, weights = weight)
cox_model_clustered2 <- coxph(Surv(FUds, death_lm) ~ case_control, data = LM2,  weights =weight)
cox_model_clustered3 <- coxph(Surv(FUds, death_lm) ~ case_control, data = LM3, weights = weight)

fit <- survfit(Surv(FUds, death_lm) ~ case_control, data = LM1, weights = weight)
plot(fit, fun = "cloglog", xlab = "Time", ylab = "log(-log(Survival))")

zph_model1 <-cox.zph(cox_model_clustered1)#LM1 does not meet the proportional risk assumption
print(zph_model1)
zph_model2 <-cox.zph(cox_model_clustered2)#LM2 meets the proportional risk assumption
print(zph_model2)
zph_model3 <-cox.zph(cox_model_clustered3)#LM3 does not meet the proportional risk assumption
print(zph_model3)
```

#1.2.2 PPCI: split datasets by time
```{r}
#Code is almost same with 1.2.1
#landmark1, in days 0-30
LM_ppci1<-matched_data2 %>% mutate(FUds= case_when(
      followupday <=30 ~ followupday ,
      followupday  >30 ~ 30,
      TRUE ~ NA),
       FUds=if_else(FUds==0,0.0001,FUds),
    death_lm = case_when(
     followupday >30 & death == 1 ~ 0,
      TRUE ~ death)
    )%>% group_by(matchid) %>% 
  mutate(matchid_size = n()) %>% 
  ungroup() %>% mutate(weight=ifelse(case_control==0,1 /(matchid_size-1),1))


#landmark2, within 30-90 days
LM_ppci2 <- matched_data2 %>%
  mutate(case_to_remove = ifelse(case_control == 1 & followupday <= 30 & death == 1, 1, 0)) %>%
  group_by(matchid) %>%
  mutate(case_to_remove_matchid = max(case_to_remove, na.rm = TRUE)) %>%
  ungroup() %>%
  filter(case_to_remove_matchid == 0) %>%
  mutate(control_to_remove = ifelse(case_control == 0 & followupday <= 30 & death == 1, 1, 0)) %>%
  group_by(matchid) %>%
  mutate(all_controls_dead_30days = max(control_to_remove, na.rm = TRUE)) %>%
  mutate(remove_whole_matchid = ifelse(all_controls_dead_30days == 1, 1, 0)) %>%
  ungroup() %>%
  filter(remove_whole_matchid == 0) %>%
  mutate(FUds = case_when(
    followupday <= 90 ~ followupday,
    followupday > 90 ~ 90,
    TRUE ~ NA_real_ 
  ),
  death_lm = case_when(
    followupday > 90 & death == 1 ~ 0, 
    TRUE ~ death
  ))%>% group_by(matchid) %>% 
  mutate(matchid_size = n()) %>% 
  ungroup() %>% mutate(weight=ifelse(case_control==0,1 /(matchid_size-1),1))

#landmark3, 90 days to 1 year
LM_ppci3 <- matched_data2 %>%
  mutate(case_to_remove = ifelse(case_control == 1 & followupday <= 90 & death == 1, 1, 0)) %>%
  group_by(matchid) %>%
  mutate(case_to_remove_matchid = max(case_to_remove, na.rm = TRUE)) %>%
  ungroup() %>%
  filter(case_to_remove_matchid == 0) %>%
  mutate(control_to_remove = ifelse(case_control == 0 & followupday <= 90 & death == 1, 1, 0)) %>%
  group_by(matchid) %>%
  mutate(all_controls_dead_90days = max(control_to_remove, na.rm = TRUE)) %>%
  mutate(remove_whole_matchid = ifelse(all_controls_dead_90days == 1, 1, 0)) %>%
  ungroup() %>%
  filter(remove_whole_matchid == 0) %>% 
  mutate(FUds=followupday,death_lm=death)%>% group_by(matchid) %>% 
  mutate(matchid_size = n()) %>% 
  ungroup() %>% mutate(weight=ifelse(case_control==0,1 /(matchid_size-1),1))

#0-1y
LM_ppci3_1 <- matched_data2 %>% mutate(FUds= case_when(
      followupday <=365 ~ followupday ,
      followupday  >365 ~ 365,
      TRUE ~ NA),
      FUds=if_else(FUds==0,0.0001,FUds),
    death_lm = case_when(
     followupday >365 & death == 1 ~ 0,
      TRUE ~ death)
    )%>% group_by(matchid) %>% 
  mutate(matchid_size = n()) %>% 
  ungroup() %>% mutate(weight=ifelse(case_control==0,1 /(matchid_size-1),1))

#1y-5y
LM_ppci3_2 <- matched_data2 %>%
  mutate(case_to_remove = ifelse(case_control == 1 & followupday <= 365 & death == 1, 1, 0)) %>%
  group_by(matchid) %>%
  mutate(case_to_remove_matchid = max(case_to_remove, na.rm = TRUE)) %>%
  ungroup() %>%
  filter(case_to_remove_matchid == 0) %>%
  mutate(control_to_remove = ifelse(case_control == 0 & followupday <= 365 & death == 1, 1, 0)) %>%
  group_by(matchid) %>%
  mutate(all_controls_dead_90days = max(control_to_remove, na.rm = TRUE)) %>%
  mutate(remove_whole_matchid = ifelse(all_controls_dead_90days == 1, 1, 0)) %>%
  ungroup() %>%
  filter(remove_whole_matchid == 0) %>% 
  mutate(FUds=followupday,death_lm=death)%>% group_by(matchid) %>% 
  mutate(matchid_size = n()) %>% 
  ungroup() %>% mutate(weight=ifelse(case_control==0,1 /(matchid_size-1),1))


#landmark1,0-90 days
LM_ppci4<-matched_data2 %>% mutate(FUds= case_when(
      followupday <=90 ~ followupday ,
      followupday  >90 ~ 90,
      TRUE ~ NA),
       FUds=if_else(FUds==0,0.0001,FUds),
    death_lm = case_when(
     followupday >90 & death == 1 ~ 0,
      TRUE ~ death)
    )%>% group_by(matchid) %>% 
  mutate(matchid_size = n()) %>% 
  ungroup() %>% mutate(weight=ifelse(case_control==0,1 /(matchid_size-1),1))

```
# 1.2.3 Fibrinolysis: split datasets by time (same logic as above, using matched_data3)

#1.2.4 Conservative therapy: split datasets by time(same logic as above, using matched_data4)

#2.1 Plot Figure1 cumulative survival curve
```{r}

custom_theme <- function() {
  theme(
    text = element_text(family = "serif", size = 12),  
    panel.border = element_blank(),  
    axis.line.x = element_line(size = 0.5),  
    axis.line.y = element_line(size = 0.5),  
    axis.line = element_line(size = 0.5),              
    axis.ticks = element_line(size = 0.5),             
    legend.position = "top",                          
    legend.title = element_blank(),                   
    panel.grid.major = element_blank(),                
    panel.grid.minor = element_blank(),                
    axis.text = element_text(size = 10),                
    axis.title = element_text(size = 12)               
  )
}

plot_survival_curve <- function(data, palette_colors, legend_labels) {

  surv_fit <- survfit(Surv(followupday, death) ~ case_control, data = data, weights = weight)
  

  plot <- ggsurvplot(
    surv_fit, data = data, conf.int = TRUE,
    palette = palette_colors, 
    xlab = "Follow-up days", ylab = "Death(%)",
    ggtheme = theme_bw(), legend.labs = legend_labels,
    fun = function(x) 100 * (1 - x)
  )
  

  plot$plot <- plot$plot + custom_theme() +
    scale_y_continuous(limits = c(0, 30)) +
    scale_x_continuous(
      breaks = c(0, 30, 90, 365, 365 * 2, 365 * 3, 365 * 4, 365 * 5),
      labels = c(0, 30, 90, 365, 365 * 2, 365 * 3, 365 * 4, 365 * 5),
      expand = c(0.05, 0)  
    ) +
    geom_vline(xintercept = 30, linetype = "dashed", color = "gray") +
    geom_vline(xintercept = 90, linetype = "dashed", color = "gray") +
    guides(color = guide_legend(nrow = 2)) +  
    theme(
      legend.position = "top",
      legend.text = element_text(size = 10),
      legend.key.height = unit(0.5, "cm"),  
      legend.spacing.y = unit(0.2, "cm"),   
      legend.margin = margin(t = 15, b = -40, unit = "pt") 
    )
  
  return(plot)
}


p1 <- plot_survival_curve(
  matched_data1,
  palette_colors = c("#2E9FDF", "#CA6F62"),
  legend_labels = c("STEMI Patients", "Age- and Sex-Matched General Population")
)

p2 <- plot_survival_curve(
  matched_data2,
  palette_colors = c("#2E9FDF", "#CA6F62"),
  legend_labels = c("Patients treated with PPCI", "Age- and Sex-Matched General Population")
)

p3 <- plot_survival_curve(
  matched_data3,
  palette_colors = c("#2E9FDF", "#CA6F62"),
  legend_labels = c("Patients treated with Fibrinolysis", "Age- and Sex-Matched General Population")
)

p4 <- plot_survival_curve(
  matched_data4,
  palette_colors = c("#2E9FDF", "#CA6F62"),
  legend_labels = c("Patients treated without reperfusion", "Age- and Sex-Matched General Population")
)

p<-grid.arrange(p1$plot,p4$plot, p3$plot, p2$plot,ncol = 2)
ggsave("Figure1.pdf",plot=p,width=40,height=15, units = "cm")

```
#2.2 calculated weighted mortality and rate difference
```{r}
library(parallel)
library(boot)

# Define function to calculate rate difference
rate_diff_func <- function(data, indices) {
  # Sample data based on indices
  sample_data <- data[indices, ]
  
  # Calculate rate difference between cases and controls
  rate_difference_bh <- weighted.mean(
    sample_data$death_lm[sample_data$case_control == 1], 
    sample_data$weight[sample_data$case_control == 1]
  ) - weighted.mean(
    sample_data$death_lm[sample_data$case_control == 0], 
    sample_data$weight[sample_data$case_control == 0]
  )
  
  return(rate_difference_bh)
}

# Calculate weighted mortality rates
calculate_weighted_mortality <- function(data) {
  # Calculate weighted mortality for case and control groups
  weighted_case_mortality <- weighted.mean(
    data$death_lm[data$case_control == 1], 
    data$weight[data$case_control == 1]
  )
  weighted_control_mortality <- weighted.mean(
    data$death_lm[data$case_control == 0], 
    data$weight[data$case_control == 0]
  )
  
  return(data.frame(
    weighted_case_mortality = weighted_case_mortality,
    weighted_control_mortality = weighted_control_mortality
  ))
}

# List of datasets
datasets <- list(
 LM1 = LM1, LM2 = LM2, LM3 = LM3, 
 LM_ppci1 = LM_ppci1, LM_ppci2 = LM_ppci2, LM_ppci3 = LM_ppci3, 
  LM_f1 = LM_f1, LM_f2 = LM_f2, LM_f3 = LM_f3, 
  LM_b1 = LM_b1, LM_b2 = LM_b2, LM_b3 = LM_b3
)

# Calculate weighted mortality rates and confidence intervals
results <- lapply(names(datasets), function(name) {
  data <- datasets[[name]]
  
  # Precompute mortality rates
  mortality <- calculate_weighted_mortality(data)
  mortality$dataset <- name
  
  # Perform bootstrap with default core settings
  bootstrap <- boot(
    data = data, 
    statistic = rate_diff_func, 
    R = 1000, # Adjust R for speed vs. accuracy
    parallel = "multicore"
  )
  
  # Calculate confidence intervals and handle cases where intervals cannot be computed
  ci_diff <- tryCatch({
    boot.ci(bootstrap, type = "perc")
  }, error = function(e) NULL)
  
  # Add rate difference and confidence intervals or NA if intervals cannot be calculated
  mortality$rate_difference <- mean(bootstrap$t)
  mortality$ci_diff_lower <- if (!is.null(ci_diff)) ci_diff$perc[4] else NA
  mortality$ci_diff_upper <- if (!is.null(ci_diff)) ci_diff$perc[5] else NA
  
  return(mortality)
})

# Combine results into a single dataset
final_results <- do.call(rbind, results)
final_results


export_to_excel(final_results, "/Users/yilin/Documents/文章/心肌梗死病例对照/数据分析/结果/表/Table2.xlsx", "weight")


create_table_one <- function(data,datasets_name){
  tableOne <- CreateTableOne(vars ="death_lm", factorVars ="death_lm",strata = c("case_control"),data =data, includeNA = F,addOverall=T)
tab <- as.data.frame(print(tableOne,showAllLevels = F, quote = FALSE, noSpaces = TRUE, missing = TRUE,contDigits = 1))
tab$dataset<-datasets_name
return(tab)
}
all_table<-lapply(names(datasets),function(name){create_table_one(datasets[[name]],name)})
final_table<-do.call(rbind,all_table)


export_to_excel(final_table, "/Users/yilin/Documents/文章/心肌梗死病例对照/数据分析/结果/表/TableS5.xlsx", "Sheet2")
```
#2.3Flexible parametric modeling
```{r}
library(rstpm2)
extract_hr_p <- function(model, model_name) {
  model_summary <- summary(model)

  coef_value <- coef(model_summary)["case_control", "Estimate"]
  se_value <- coef(model_summary)["case_control", "Std. Error"]
  p_value <- coef(model_summary)["case_control", "Pr(z)"]

  HR <- exp(coef_value)
  HR_lower <- exp(coef_value - 1.96 * se_value)
  HR_upper <- exp(coef_value + 1.96 * se_value)

  result <- data.frame(
    model_name = model_name,
    HR = HR,
    HR_lower = HR_lower,
    HR_upper = HR_upper,
    p = p_value
  )
  return(result)
}

#df was chosen according to the AIC guidelines.
#ppci
# 0-30 days
model_0_30 <- stpm2(Surv(FUds, death_lm) ~ case_control+ cluster(matchid_size), df =3, data = LM_ppci1)
AIC(model_0_30)
summary(model_0_30)

# 30-90 days
model_30_90 <- stpm2(Surv(FUds, death_lm) ~ case_control+ cluster(matchid_size), df =5, 
                     data = LM_ppci2)
summary(model_30_90)

# 90-1year
model_90_1y <- stpm2(Surv(FUds, death_lm) ~ case_control+ cluster(matchid_size), df =3,  data = LM_ppci3_1)
summary(model_90_1y)
# 1 year-5 years
model_1y_5y <- stpm2(Surv(FUds, death_lm) ~ case_control+ cluster(matchid_size), df =3, data = LM_ppci3_2)

summary(model_1y_5y)

# 90days -5 years
model_90_5y <- stpm2(Surv(FUds, death_lm) ~ case_control+ cluster(matchid_size), df =5, 
                     data = LM_ppci3)
AIC(model_90_5y)
summary(model_90_5y)

result_0_30 <- extract_hr_p(model_0_30, "model_0_30")
result_30_90 <- extract_hr_p(model_30_90, "model_30_90")
result_90_5y <- extract_hr_p(model_90_5y, "model_90_5y")

results_df <- rbind(result_0_30,result_30_90, result_90_5y)

print(results_df)
export_to_excel(results_df, "/Users/yilin/Documents/文章/心肌梗死病例对照/数据分析/结果/表/Table2.xlsx", "ppci")

#Firbrinolysis
# As this dataset was fully matched using a 1:5 ratio, clustering by matchid_size is unnecessary.
# 0-30 days
model_0_30 <- stpm2(Surv(FUds, death_lm) ~ case_control, df =3,data = LM_f1)
AIC(model_0_30)
summary(model_0_30)
# 30-90 days
model_30_90 <- stpm2(Surv(FUds, death_lm) ~ case_control, df =5, data = LM_f2)
AIC(model_30_90)
summary(model_30_90)
# 90days-5years
model_90_5y <- stpm2(Surv(FUds, death_lm) ~ case_control, df =4,data = LM_f3)
AIC(model_90_5y)
summary(model_90_5y)

result_0_30 <- extract_hr_p(model_0_30, "model_0_30")
result_30_90 <- extract_hr_p(model_30_90, "model_30_90")
result_90_5y <- extract_hr_p(model_90_5y, "model_90_5y")

# 合并两个结果为一个数据框
results_df1 <- rbind(result_0_30,result_30_90, result_90_5y)

# 查看合并后的数据框
print(results_df1)
export_to_excel(results_df1, "/Users/yilin/Documents/文章/心肌梗死病例对照/数据分析/结果/表/Table2.xlsx", "fibri")

#Conservative therapy
# 0-30days
model_0_30 <- stpm2(Surv(FUds, death_lm) ~ case_control+ cluster(matchid_size), df =4,data = LM_b1)
AIC(model_0_30)
summary(model_0_30)
# 30-90days
model_30_90 <- stpm2(Surv(FUds, death_lm) ~ case_control+ cluster(matchid_size), df =5, data = LM_b2)
AIC(model_30_90)
summary(model_30_90)
# 90days-5years
model_90_5y <- stpm2(Surv(FUds, death_lm) ~ case_control+ cluster(matchid_size), df =4,data = LM_b3)
AIC(model_90_5y)
summary(model_90_5y)

result_0_30 <- extract_hr_p(model_0_30, "model_0_30")
result_30_90 <- extract_hr_p(model_30_90, "model_30_90")
result_90_5y <- extract_hr_p(model_90_5y, "model_90_5y")


results_df2 <- rbind(result_0_30,result_30_90, result_90_5y)


print(results_df2)
export_to_excel(results_df2, "/Users/yilin/Documents/文章/心肌梗死病例对照/数据分析/结果/表/Table2.xlsx", "baoshou")

#STEMI patients
#0-30 days
model_0_30 <- stpm2(Surv(FUds, death_lm) ~ case_control+ cluster(matchid_size), df =4,data = LM1)
AIC(model_0_30)
summary(model_0_30 )
#30-90days
model_30_90 <- stpm2(Surv(FUds, death_lm) ~ case_control+ cluster(matchid_size), df =5, data = LM2)
AIC(model_30_90 )
#90days-5 years
model_90_5y <- stpm2(Surv(FUds, death_lm) ~ case_control+ cluster(matchid_size), df =5,data = LM3)
AIC(model_90_5y)
summary(model_90_5y)
result_0_30 <- extract_hr_p(model_0_30, "model_0_30")
result_30_90 <- extract_hr_p(model_30_90, "model_30_90")
result_90_5y <- extract_hr_p(model_90_5y, "model_90_5y")


results_df <- rbind(result_0_30,result_30_90, result_90_5y)


print(results_df)
export_to_excel(results_df, "/Users/yilin/Documents/文章/心肌梗死病例对照/数据分析/结果/表/Table2.xlsx", "all")
```
#2.4 TableS7 Adding age and corvarites into models
```{r}
covariates <- c("diabetes", "hyp",  "smoke")
#ppci
#only adjust age
# 0-30 days
model_0_30 <- stpm2(Surv(FUds, death_lm) ~ case_control+age+ cluster(matchid_size), df =3,data = LM_ppci1)
# 30-90 days
model_30_90 <- stpm2(Surv(FUds, death_lm) ~ case_control+age+ cluster(matchid_size), df =5, data = LM_ppci2)
# 90 days-5 years
model_90_5y <- stpm2(Surv(FUds, death_lm) ~ case_control+age+ cluster(matchid_size), df =3, data = LM_ppci3)
# Extract results for each model
result_0_30 <- extract_hr_p(model_0_30, "model_0_30")
result_30_90 <- extract_hr_p(model_30_90, "model_30_90")
result_90_5y <- extract_hr_p(model_90_5y, "model_90_5y")

# Adjusted models with covariates
# 0-30 days
model_0_30 <- LM_ppci1 %>%
  filter(!(diabetes=="")&!(hyp=="")&!(smoke=="")) %>% stpm2(Surv(FUds, death_lm) ~case_control+age+diabetes+hyp+edu+smoke+cluster(matchid_size), df =3, data = .)
# 30-90 days
model_30_90 <- LM_ppci2%>% filter(!(diabetes=="")&!(hyp=="")&!(smoke=="")) %>%stpm2(Surv(FUds, death_lm) ~ case_control+age+diabetes+hyp+edu+smoke+ cluster(matchid_size), df =5, data =. )
# 90 days-5 years
model_90_5y <- LM_ppci3%>% filter(!(diabetes=="")&!(hyp=="")&!(smoke=="")) %>%stpm2(Surv(FUds, death_lm) ~ case_control+age+diabetes+hyp+edu+smoke+ cluster(matchid_size), df =5, data = .)
# Extract adjusted results
result_0_30a <- extract_hr_p(model_0_30, "model_0_30")
result_30_90a <- extract_hr_p(model_30_90, "model_30_90")
result_90_5ya <- extract_hr_p(model_90_5y, "model_90_5y")
# Combine results
results_df <- rbind(result_0_30,result_30_90, result_90_5y,result_0_30a,result_30_90a, result_90_5ya)

export_to_excel(results_df, "/Users/yilin/Documents/文章/心肌梗死病例对照/数据分析/结果/表/TableS7.xlsx", "ppci")

#Thrombolysis therapy
#only adjust age
# 0-30 days
model_0_30 <- stpm2(Surv(FUds, death_lm) ~ case_control+age, df =3,data = LM_f1)
# 30-90 days
model_30_90 <- stpm2(Surv(FUds, death_lm) ~ case_control+age, df =5, data = LM_f2)
# 90 days-5 years
model_90_5y <- stpm2(Surv(FUds, death_lm) ~ case_control+age, df =4,data = LM_f3)
# Extract results
result_0_30 <- extract_hr_p(model_0_30, "model_0_30")
result_30_90 <- extract_hr_p(model_30_90, "model_30_90")
result_90_5y <- extract_hr_p(model_90_5y, "model_90_5y")

# Adjusted models with covariates
# 0-30 days
model_0_30 <- LM_f1%>% filter(!(diabetes=="")&!(hyp=="")&!(edu=="")&!(smoke=="")) %>%stpm2(Surv(FUds, death_lm) ~ case_control+age+diabetes+hyp+edu+smoke, df =3,data =. )
# 30-90 days
model_30_90 <- LM_f2%>% filter(!(diabetes=="")&!(hyp=="")&!(edu=="")&!(smoke=="")) %>%stpm2(Surv(FUds, death_lm) ~ case_control+age+diabetes+hyp+edu+smoke, df =5, data = .)
# 90 days-5 years
model_90_5y <- LM_f3%>% filter(!(diabetes=="")&!(hyp=="")&!(edu=="")&!(smoke=="")) %>%stpm2(Surv(FUds, death_lm) ~ case_control+age+diabetes+hyp+edu+smoke, df =4,data = .)

result_0_30a <- extract_hr_p(model_0_30, "model_0_30")
result_30_90a <- extract_hr_p(model_30_90, "model_30_90")
result_90_5ya <- extract_hr_p(model_90_5y, "model_90_5y")

results_df1 <- rbind(result_0_30,result_30_90, result_90_5y,result_0_30a,result_30_90a, result_90_5ya)
export_to_excel(results_df1, "/Users/yilin/Documents/文章/心肌梗死病例对照/数据分析/结果/表/TableS7.xlsx", "fibri")

# Conservative therapy
#only adjust age
# 0-30 days
model_0_30 <- stpm2(Surv(FUds, death_lm) ~ case_control+age+ cluster(matchid_size), df =4,data = LM_b1)
# 30-90 days
model_30_90 <- stpm2(Surv(FUds, death_lm) ~ case_control+age+ cluster(matchid_size), df =5, data = LM_b2)
# 90 days-5 years
model_90_5y <- stpm2(Surv(FUds, death_lm) ~ case_control+age+ cluster(matchid_size), df =4,data = LM_b3)

result_0_30 <- extract_hr_p(model_0_30, "model_0_30")
result_30_90 <- extract_hr_p(model_30_90, "model_30_90")
result_90_5y <- extract_hr_p(model_90_5y, "model_90_5y")

# Adjusted models with covariates
# 0-30 days
model_0_30 <- LM_b1%>% filter(!(diabetes=="")&!(hyp=="")&!(edu=="")&!(smoke=="")) %>%stpm2(Surv(FUds, death_lm) ~ case_control+age+diabetes+hyp+edu+smoke+ cluster(matchid_size), df =4,data =.)

# 30-90 days
model_30_90 <- LM_b2%>% filter(!(diabetes=="")&!(hyp=="")&!(edu=="")&!(smoke=="")) %>%stpm2(Surv(FUds, death_lm) ~ case_control+age+diabetes+hyp+edu+smoke+ cluster(matchid_size), df =5, data =.)
# 90 days-5 years
model_90_5y <- LM_b3%>% filter(!(diabetes=="")&!(hyp=="")&!(edu=="")&!(smoke=="")) %>%stpm2(Surv(FUds, death_lm) ~ case_control+age+diabetes+hyp+edu+smoke+ cluster(matchid_size), df =4,data =.)

result_0_30a <- extract_hr_p(model_0_30, "model_0_30")
result_30_90a <- extract_hr_p(model_30_90, "model_30_90")
result_90_5ya <- extract_hr_p(model_90_5y, "model_90_5y")

results_df2 <- rbind(result_0_30,result_30_90, result_90_5y,result_0_30a,result_30_90a, result_90_5ya)

export_to_excel(results_df2, "/Users/yilin/Documents/文章/心肌梗死病例对照/数据分析/结果/表/TableS7.xlsx", "baoshou")

#All STEMI patients
#only adjust age
# 0-30 days
model_0_30 <- stpm2(Surv(FUds, death_lm) ~ case_control+age+ cluster(matchid_size), df =4, data = LM1)
# 30-90 days
model_30_90 <- stpm2(Surv(FUds, death_lm) ~ case_control+age+ cluster(matchid_size), df =5, data = LM2)
# 90 days-5 years
model_90_5y <- stpm2(Surv(FUds, death_lm) ~ case_control+age+ cluster(matchid_size), df =5, data = LM3)

result_0_30 <- extract_hr_p(model_0_30, "model_0_30")
result_30_90 <- extract_hr_p(model_30_90, "model_30_90")
result_90_5y <- extract_hr_p(model_90_5y, "model_90_5y")

# Adjusted models with covariates
# 0-30 days
model_0_30 <- LM1%>% filter(!(diabetes=="")&!(hyp=="")&!(edu=="")&!(smoke=="")) %>%stpm2(Surv(FUds, death_lm) ~ case_control+age+diabetes+hyp+edu+smoke+ cluster(matchid_size), df =4, data =.)
# 30-90 days
model_30_90 <- LM2%>% filter(!(diabetes=="")&!(hyp=="")&!(edu=="")&!(smoke=="")) %>%stpm2(Surv(FUds, death_lm) ~ case_control+age+diabetes+hyp+edu+smoke+ cluster(matchid_size), df =5, data =.)
# 90 days-5 years
model_90_5y <- LM3%>% filter(!(diabetes=="")&!(hyp=="")&!(edu=="")&!(smoke=="")) %>%stpm2(Surv(FUds, death_lm) ~ case_control+age+diabetes+hyp+edu+smoke+ cluster(matchid_size), df =5, data =.)

result_0_30a <- extract_hr_p(model_0_30, "model_0_30")
result_30_90a <- extract_hr_p(model_30_90, "model_30_90")
result_90_5ya <- extract_hr_p(model_90_5y, "model_90_5y")

results_df <- rbind(result_0_30,result_30_90, result_90_5y,result_0_30a,result_30_90a, result_90_5ya)

export_to_excel(results_df, "/Users/yilin/Documents/文章/心肌梗死病例对照/数据分析/结果/表/TableS7.xlsx", "all")
```
